Ensemble Stability of Biological Networks

### 2014-09-26 paper.tex
define indicator function

A quality which is of interest to us is robustness or structural stability \cite{Smale1967}, which requires the determination of whether or not a given dynamical system that is determined to be stable remains stable under a perturbation to one or more of its defining parameters.  We will quantify this as the probability that, if some property holds for a set of parameters, it will continue to hold if we make a random perturbation about those parameter values. To do so, we will introduce, in addition to the probability distribution $\mu$ described above, a family of probability distributions $\mu'$ such that $\mu'(x,y)$ encodes the conditional probability that a system with a parameter value $x$ will have its parameter values changed to $y$ under a perturbation.  For our biological models, we will be interested in large perturbations rather than the small or infinitesimal perturbations usually considered in the theory of dynamical systems.  Then, given a binary random variable $q$, we define its robustness as the following conditional probability:
\begin{align}\label{eq:robustness}
  R (q) =
  \frac{\int_S d\mu(x) \int_S d\mu'(x,y) \mathbf{1}_q(x) \mathbf{1}_q(y)}
  {\int_S d\mu(x) \mathbf{1}_q(x)}
\end{align}

>>>>

A quality which is of interest to us is robustness or structural stability \cite{Smale1967}, which requires the determination of whether or not a given dynamical system that is determined to be stable remains stable under a perturbation to one or more of its defining parameters.  We will quantify this as the probability that, if some property holds for a set of parameters, it will continue to hold if we make a random perturbation about those parameter values. To do so, we will introduce, in addition to the probability distribution $\mu$ described above, a family of probability distributions $\mu'$ such that $\mu'(x,y)$ encodes the conditional probability that a system with a parameter value $x$ will have its parameter values changed to $y$ under a perturbation.  For our biological models, we will be interested in large perturbations rather than the small or infinitesimal perturbations usually considered in the theory of dynamical systems.  Then, given a binary random variable $q$, we define its robustness as the following conditional probability where $\mathbf{1}_q(x)$ is the standard indicator function equal to $1$ when $x$ satisfies $q$ and $0$ otherwise:
\begin{align}\label{eq:robustness}
  R (q) =
  \frac{\int_S d\mu(x) \int_S d\mu'(x,y) \mathbf{1}_q(x) \mathbf{1}_q(y)}
  {\int_S d\mu(x) \mathbf{1}_q(x)}
\end{align}
